The shape of kelp: environmental influences on kelp morphology

### 2018-10-29 chapter_2.Rmd
script did not commit in last commit. Re-try. depth morphology data set added

@@

### Abiotic correlations

>>>>

```{r, echo= FALSE, message=FALSE, warning=FALSE, fig.cap="Boxplots representing the different _Ecklonia maxima_ morphometrics between deep and shallow water sites measured around the Western Cape coastline, with the X-axis depicting the specific morphology measured, with units provided. Boxplots represent the minimum, 25^th^ percentile, median and 75^th^ percentile of the morphometrics measured. Interquartile range can be deduced as the different between the 75^th^ and 25^th^ percentiles, and dots represent outliers in the data. Sites are ordered sequentially on the Y-axis by location along the coast. The top site is St. Helena Bay and is located at the north western boundary, and Betty’s Bay as the bottom site is located at the south eastern boundary, from our sample region.", fig.height=8, fig.width=12, fig.pos="H"}

# load data
comp_df <- read.csv("data/morph_comp.csv", sep = ";")

# remove unnecessary columns
comp_df <- subset(comp_df, select = -c(3))

# alter dataframe for more friendly plotting
comp_gather <- gather(comp_df, "Morphology", "Measurement", 3:12, na.rm = TRUE)

# Replace morphology names
comp_gather <- comp_gather %>%
  mutate(Morphology = replace(Morphology, 
                              Morphology == "fond_mass", "Frond mass (kg)")) %>% 
  mutate(Morphology = replace(Morphology, 
                              Morphology == "primary_length", "Primary length (cm)")) %>% 
  mutate(Morphology = replace(Morphology, 
                              Morphology == "primary_width", "Primary width (cm)")) %>% 
  mutate(Morphology = replace(Morphology, 
                              Morphology == "frond_length", "Frond length (cm)")) %>% 
  mutate(Morphology = replace(Morphology, 
                              Morphology == "stipe_mass", "Stipe mass (kg)")) %>% 
  mutate(Morphology = replace(Morphology, 
                              Morphology == "stipe_length", "Stipe length (cm)")) %>% 
  mutate(Morphology = replace(Morphology, 
                              Morphology == "stipe_circ", "Stipe circumference (cm)")) %>% 
  mutate(Morphology = replace(Morphology, 
                              Morphology == "tufts", "Number of tufts")) %>% 
  mutate(Morphology = replace(Morphology, 
                              Morphology == "epi_length", "Epiphyte length (cm)")) %>% 
  mutate(Morphology = replace(Morphology, 
                              Morphology == "total_length", "Total length (cm)"))

comp_gather_mean <- comp_gather %>%
  group_by(site, Morphology) %>%
  summarise(mean = mean(Measurement, na.rm = TRUE)) %>%
  ungroup()

positionsComp <- c("Kalk Bay", 
                  "Miller's Point", "Buffels Bay", "Soetwater", "Kommetjie")

# Plot morphologies

ggplot(data = comp_gather, aes(x = site, y = Measurement, fill = depth)) +
  geom_boxplot() +
  facet_wrap(~Morphology, scales = "free_x", strip.position = "bottom", ncol = 5) +
  coord_flip() + 
  scale_x_discrete(limits = positionsComp) +
  theme(strip.background = element_blank(), strip.placement = "outside", text = element_text(size   = 4.5)) +
  xlab("Site") +
  ylab("Morphology measurement") + 
  theme_bw()

### Abiotic correlations
```{r, echo= FALSE, message=FALSE, warning=FALSE, results="hide"}

@@
